Computing Restricted Isometry Constants via \\ Mixed-Integer Semidefinite Programming

### 2016-03-23 RIP-MISDP-Paper/RIP-MISDP_optimization-online.tex
added amsart-version for optimization online

\documentclass[journal,onecolumn]{IEEEtran}

@@

\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue,bookmarks=false,hypertexnames=false,
  pdftitle={Computing Restricted Isometry Constants via Mixed-Integer Semidefinite Programming},
  % pdftitle={Computing Restricted Isometry Constants via Mixed Integer Semidefinite Programming},
  pdfauthor={T. Gally, and M. E. Pfetsch}]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{lemma}[theorem]{Lemma}

@@

% prevent tables from being broken too early
\xentrystretch{-0.22}

@@

\title{Computing Restricted Isometry Constants via Mixed-Integer Semidefinite Programming}
\author{Tristan~Gally and Marc~E.~Pfetsch
  \thanks{This work was supported by the German Research Foundation (DFG) through Collaborative Research Center 805 and Priority Program 1798.}
  \thanks{The  authors  are  with  the  Research  Group  Optimization,  TU
    Darmstadt, Dolivostr.\ 15,
  Darmstadt  64293,  Germany  (e-mail:  gally@opt.tu-darmstadt.de;
  pfetsch@opt.tu-darmstadt.de).}}

@@

\IEEEpeerreviewmaketitle

\begin{IEEEkeywords}
 Compressed Sensing, Restricted Isometry Property, Mixed-Integer Semidefinite Programming
\end{IEEEkeywords}

@@

\IEEEPARstart{F}{inding} a sparsest solution of an underdetermined system of linear
equations is one key problem in compressed sensing and has been
thoroughly investigated in recent years. Given a matrix $A \in \R^{m \times n}$ with $m \leq n$ and 
right-hand side $b \in \R^m$, the core problem is
\begin{align}\label{l0min}
 \min \quad & \Norm{x}{0} \tag{$P_0$}\\
 \text{s.t.} \quad & Ax = b, \nonumber
\end{align}
where $\Norm{x}{0}$ denotes the number of nonzero components of~$x$. This
problem is \NP-hard, see Garey and
Johnson~\cite{GareyJohnson}. One key observation in compressed sensing is
that a solution of~\eqref{l0min} can be found by solving the following
convex optimization problem, if certain conditions are fulfilled:
\begin{align}\label{l1min}
 \min \quad & \Norm{x}{1} \tag{$P_1$}\\
 \text{s.t.} \quad & Ax = b. \nonumber
\end{align}
In fact, this so-called \emph{basis pursuit} problem can be reformulated as
a linear program (LP) and efficient specialized solution algorithms are
available both in theory and practice: as an extremely selected list
consider the articles~\cite{BecBC11,CheDS99,OsbPT00,vdBF08} and the
practical comparison in~\cite{LorPT15}.
% Note: do not write out author names to keep text short at this place.

@@

\begin{definition}\label{ripdef}
  The \emph{restricted isometry property} (RIP) of order~$k$ holds for a
  matrix $A \in \R^{m \times n}$ with constant~$\delta \geq 0$, if
  \begin{equation}\label{rip}
    (1 - \delta) \Norm{x}{2}^2 \leq \Norm{Ax}{2}^2 \leq (1+\delta) \Norm{x}{2}^2
    \quad\text{for all }x \in \Sigma_k \define \{x \in \R^n \suchthat \Norm{x}{0} \leq k\}.
  \end{equation}
\end{definition}

@@

\begin{IEEEbiographynophoto}{Tristan Gally}
obtained a B.Sc. and an M.Sc. degree in mathematics with economics
from TU Darmstadt, Germany, in 2011 and 2013, respectively. Since
02/2014 he is a doctoral candidate at TU Darmstadt working as a
Researcher in the Collaborative Research Center 805, funded by the
German Research Foundation (DFG). His research interests are mainly
in mixed-integer semidefinite programming with applications in
compressed sensing and truss topology design.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Marc E. Pfetsch}
  obtained a Diploma degree in mathematics from the University of
  Heidelberg, Germany, in 1997. He received a PhD degree in
  mathematics in 2002 and the Habilitation degree in 2008 from TU
  Berlin, Germany. From 2008 to 2012 he was a Full Professor for
  Mathematical Optimization at TU Braunschweig, Germany. Since 04/2012
  he has been a Full Professor for Discrete Optimization at TU
  Darmstadt, Germany. His research interests are mostly in discrete
  optimization, in particular symmetry in integer programs, compressed
  sensing, and algorithms for mixed integer programs.
\end{IEEEbiographynophoto}
\vfill
\mbox{}

\newpage
\appendix{\input{tables/matrixList}}

>>>>

\documentclass[11pt,a4paper]{amsart}

@@

\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue,bookmarks=false,hypertexnames=false,
  pdftitle={Computing Restricted Isometry Constants via Mixed-Integer Semidefinite Programming},
  pdfauthor={T. Gally, and M. E. Pfetsch}]{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

@@

% prevent tables from being broken too early
\xentrystretch{-0.4}

@@

\title[Computing Restricted Isometry Constants via MISDP]{Computing Restricted Isometry Constants via \\ Mixed-Integer Semidefinite Programming}
\author[T. Gally]{Tristan Gally}
\author[M. E. Pfetsch]{Marc E. Pfetsch}

\address{Tristan Gally \\ Technische Universit\"at Darmstadt, Department of Mathematics\\ Dolivostra\ss e 15, 64293 Darmstadt, Germany}
\email{gally@mathematik.tu-darmstadt.de}
\address{Marc E. Pfetsch \\ Technische Universit\"at Darmstadt, Department of Mathematics\\ Dolivostra\ss e 15, 64293 Darmstadt, Germany}
\email{pfetsch@mathematik.tu-darmstadt.de}

@@

\smallskip
\noindent \textbf{Keywords.}
Compressed Sensing, Restricted Isometry Property, Mixed-Integer Semidefinite Programming

@@

Finding a sparsest solution of an underdetermined system of linear
equations is one key problem in compressed sensing and has been
thoroughly investigated in recent years. Given a matrix $A \in \R^{m \times n}$ with $m \leq n$ and 
right-hand side $b \in \R^m$, the core problem is
\begin{align}\label{l0min}
 \min \quad & \Norm{x}{0} \tag{$P_0$}\\
 \text{s.t.} \quad & Ax = b, \nonumber
\end{align}
where $\Norm{x}{0}$ denotes the number of nonzero components of~$x$. This
problem is \NP-hard, see Garey and
Johnson~\cite{GareyJohnson}. One key observation in compressed sensing is
that a solution of~\eqref{l0min} can be found by solving the following
convex optimization problem, if certain conditions are fulfilled:
\begin{align}\label{l1min}
 \min \quad & \Norm{x}{1} \tag{$P_1$}\\
 \text{s.t.} \quad & Ax = b. \nonumber
\end{align}
In fact, this so-called \emph{basis pursuit} problem can be reformulated as
a linear program (LP) and efficient specialized solution algorithms are
available both in theory and practice: as an extremely selected list
consider the articles~\cite{BecBC11,CheDS99,OsbPT00,vdBF08} and the
practical comparison in~\cite{LorPT15}.
% Note: do not write out author names to keep text short at this place.

@@

\begin{definition}\label{ripdef}
  The \emph{restricted isometry property} (RIP) of order~$k$ holds for a
  matrix $A \in \R^{m \times n}$ with constant~$\delta \geq 0$, if
  \begin{equation}\label{rip}
    (1 - \delta) \Norm{x}{2}^2 \leq \Norm{Ax}{2}^2 \leq (1+\delta) \Norm{x}{2}^2
  \end{equation}
  for all $x \in \Sigma_k \define \{x \in \R^n \suchthat \Norm{x}{0} \leq k\}$.
\end{definition}

@@

\appendix
\section*{Appendix}
\input{tables/matrixList_optimization-online}
